---
title: "Week 12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# Same data clean up as last week.

week_12 <- shaming %>% 
  mutate(age = 2006 - birth_year) %>% 
  mutate(treatment = fct_relevel(treatment, "Control")) %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(-general_04, -no_of_names, -birth_year, -hh_size) 

week_12_sample <- sample_n(week_12, 1000)
```


## Scene 1

**Prompt:** Create a fitted model object called `fit_1` using this formula or, if you want, a formula which you prefer. You are trying to model `age` as a function of various parameters.

age ~ sex + solo + primary_04 + primary_06 + treatment + sex:solo
                    
* Is this a causal or predictive model? Why? Predictive because no manipulation.

* Interpret the fitted model. 

Intercept - a female who doesn't live alone, that didn't vote in either the 04 or 06 primaries and was in hte control group.

sexMale - the predicted change in age moving from female to male is a decrease of 0.0938 yrs

soloTRUE - woman living alone lives 8.2455 more yrs

man living alone lives Intercept + sexMale + soloTRUE + soloTRUE:sexMale years.

primary_04Yes - the predicted change in age when someone votes in the 04 primary 
(possibly nonsensical, is age correlated with civic engagement?)

primary_06 - the predicted change in age when someone votes in the 06 primary 

treatment coefficients - the predicted change in age when someone undergoes some shaming treatment 

sexMale:soloTRUE - unique amplifying effect of being a man living alone, also difference-in-differences estimator (diff between diff of woman living with others --> living alone and diff of man living with others --> living alone) 

* Should we keep all these variables? And the interaction term?

No - eliminate treatment and sex.

* Are you surprised about the meaningfulness, or lack thereof, for the treatment variables?

Surprised that sex seems to have little predictive power.

```{r sc1}

# Adding more explanatory variables is controlling for the predictive power of more variables.

fit_obj <- stan_glm(age ~ solo + primary_06,
                    data = week_12_sample,
                    refresh = 0, 
                    seed = 9)

print(fit_obj, digits = 4)

```


## Scene 2

**Prompt:** Provide a posterior probability distribution for the expected difference in ages between those who live alone and those who do not. (Hint: Given that we are asking for an expected value, use `posterior_epred()`.)







